In the first and second sections, information was given about this study's aims, the reasons for the study's emergence, and the study's motivation sources. Besides, to better understand this study's background, objectives, and solutions, the necessary information was shared with the readers in both the Android and software development fields. As stated in the previous sections, the starting point of the study is the difficulties encountered in Android application development and a non-functional requirement named maintainability, which has an important role in solving these difficulties. As stated before, this study focuses on solving these problems in Android application development and how Mooncascade, a leading software development company in the region, approaches the issue of increasing maintainability. In this context, the approaches, techniques, and technologies used by the company's Android team will be discussed, and the level of effectiveness of these will be determined in terms of maintainability. At this point, the first question that comes to mind is how this effect can be determined or measured in terms of maintainability.

In this section,  the methods to evaluate and measure how effective the techniques, technologies, and other approaches used by Mooncascade's Android team are from the maintainability perspective will be explained. These assessment and measurement methods will be both quantitative and qualitative. In this way, it was aimed to evaluate with maximum efficiency by going beyond the traditional quantitative measurement techniques. The methods to be used and the contents of these methods will be presented in detail in this section. Also, why and how these methods are chosen will be stated in this section. Thus, the first of the three research questions stated in the introduction section will be answered in this section. In the 4th section, the technologies, techniques, and approaches used by Mooncascade's Android team to increase the maintainability of Android applications and eliminate the difficulties mentioned in the previous sections will be discussed. These techniques, technologies, and approaches will be evaluated in section 5 using the measurement and evaluation techniques explained in this study. Therefore, it was thought that answering the first research question here is more appropriate before answering other research questions in the upcoming sections. The remainder of this section will provide detailed information on the quantitative and qualitative measurement techniques to be applied in this study to measure maintainability in the context of Android application development. 

\subsection{Qualitative Method}
\input{chapters/3-research-methodology/3.1-qualitative-method/3.1-text}

\subsection{Maintainability Evaluation with Object-Oriented Metrics}
\label{section:3.2}
\input{chapters/3-research-methodology/3.2-quantitative-method/3.2-text}

\subsection{Summary}
\input{chapters/3-research-methodology/3.3-summary/3.3.-text}
