The rest of this document is organized as follows. In Chapter 2, brief information about the Android platform and Android SDK is given. The chapter continues with key concepts for the maintainability of software systems. Lastly, the methods and technologies used by Mooncascade's Android team to tackle the problems mentioned in the first chapter are presented. In Chapter 3, why and how the literature review was carried out within the scope of this study and the results of this literature review is shared. Also, a brief analysis of the results is presented. In Chapter 4, the methods used to achieve the primary goal of this study are presented. The contents of the survey and interviews are discussed in detail. Also, metrics used while evaluating methods and technologies used by Mooncascade's Android team in terms of maintainability are explained. Thus, the first research question will be answered in this chapter. In Chapter 5, the results for the impact of the practices that are used by Mooncascade's Android team on the maintainability of Android applications are shared. The results obtained from the Android developer survey, interviews with the case company's Android developers and evaluation with the object-oriented metrics are presented as well. Chapter 6 presents the discussion and interpretation of answers to the research questions and evaluation results obtained in the previous chapters. Outcomes of the evaluations will be shared. Also, the limitations of the study will be mentioned. The last chapter concludes this thesis, and future research opportunities are discussed.

