The second step of the qualitative evaluations carried out within this study’s scope is the interviews conducted with Mooncascade's Android team members.  The interview questions are designed to qualitatively evaluate the techniques and technologies used by Mooncascade's Android team in terms of maintainability. Also, the interviews aim to determine the importance of maintainability from the case company's point of view.  Thus, proving or disproving the study's claim that maintainability is a key concept to overcome the issues mentioned in the problem statement section would be possible. Eight questions were determined for these purposes. Below are listed the questions asked to each member of Mooncascade's Android team during these interviews:
\begin{itemize}
    \item How many years of experience do you have as an Android developer? Please specify the years in Mooncascade and other companies.
    \item How many different Android projects have you completed in Mooncascade, and how many different domains did those projects belong to?
    \item What is your understanding of maintainability in the context of software engineering?
    \item As an employee of a software development company that provides services to the different domains, what makes maintainability more essential for you?
    \item What is the importance of maintainability when developing Android applications?
    \item What is the most critical aspect for maintainability when developing Android applications (e.g. architecture, libraries, programming language, etc.)?
    \item How do you think the current technology stack of the team impacts Android applications’ maintainability? Please specify for each item below:
    \begin{itemize}
        \item Programming Languages(Kotlin/Java)
        \item Software Engineering principles (SOLID/Clean Code)
        \item Architecture (MVVM/Clean)
        \item Libraries (RxJava, Dagger 2, Apollo/Retrofit)
        \item Android Architecture Components (ViewModel, LiveData, Room, etc.)
    \end{itemize}
    \item What could be improved in our current tech stack and the principles we apply to improve the Android applications’ maintainability?
\end{itemize}

Three main criteria were taken into consideration while preparing these questions. First of all, questions were chosen to get to know about the participants' background and experience. Later, some questions were designed to learn participants' understanding of maintainability in software engineering. Lastly, questions were drafted to learn about participants' thoughts about the impact of technologies and principles used by Mooncascade on maintainability. The interview was conducted privately with each team member.  It is aimed that the data gathered through these interviews will increase the accuracy and validity of evaluations.