The first step of qualitative evaluations in this study is the Android developer survey. The fast evolution of third-party Android libraries and developers trends is vital for Android applications' maintainability because the consistency and stability of principles and third-party libraries affect maintainability. Therefore, this survey was conducted to identify current Android trends and provide support for this study's evaluation. While determining this survey's questions, priority was given to principles and technologies that affect maintainability. Although the questions are generally prepared to cover the methods used by the Mooncascade Android's team, it can be said that the questions reflect the Android technology stack in general. Also, the first question was added to the survey to learn about the competence of participants. Learning the competence of the participants is important for increasing the probability of getting more accurate results from the survey because the preferred technology and methods for Android application development differs based on the participants’ experience. The survey questions are presented below. 
\begin{itemize}
    \item How many years of professional experience do you have as an Android developer?
    \item Which programming language do you use for Android application development?
    \item What presentational design pattern do you apply to your Android apps?
    \item Do you apply Uncle Bob's Clean Architecture to your Android applications?
    \item Do you follow SOLID principles while developing Android applications?
    \item Do you follow Uncle Bob's Clean Code principles while developing Android applications?
    \item What networking library do you use?
    \item How do you handle asynchronous events in your Android applications?
    \item What dependency injection library do you use in your Android applications?
    \item Do you use Android Architecture Components in your Android applications? (LiveData, ViewModel, Room, etc.)
\end{itemize}
The questions are organised with the help of the Forms application provided by Google. The Android developer survey has been delivered to Android developers from different companies in different countries through accounts or groups of Android developer communities on social media platforms such as LinkedIn, Discord, and Twitter. The author of the study has also shared the survey with many of his colleagues/ex-colleagues working in different companies/countries.