This study's main contribution is providing comprehensive information regarding the development of large scale and enterprise Android applications through the experience of a proficient software development company, Mooncascade. Since the study topic is highly coupled to industry and industry trends, the author contributes to identifying and understanding the practices used by one of the top software development companies in the region and their impact and bringing those practices into the academy through this study. With the help of the information that this study offers, developers and researchers will know the fundamental principles and technologies required to develop state-of-the-art Android apps that have increased maintainability and quality. Thus solving the difficulties explained in the introduction section can be facilitated.

Examining white and gray literature has shown that there is no similar case study regarding Android application development. Still, some studies focus on maintainability and the quality of Android applications and solutions for challenges mentioned earlier. However, the examination has also shown that such studies lack detail and up-to-dateness. This study's valuable set of information might help fill the gap of outdatedness and lack of detail between the industry and academia in developing Android applications. Unlike most similar studies, in this study, the investigated principles and technologies will be gathered from the industry's real-life Android application development best practices. The study will include detailed information about the implementation of these principles and technologies. Apart from the main contribution, the evaluation results of presented methodologies and technologies will provide empirical data, both from the maintainability point of view and the Android developer's perspective. Lastly, the Android developer survey conducted as a part of this study can provide insights from the latest technology trends in the Android community.