\label{section:SOLID}
In the previous section, the importance of maintainability and maintenance of software systems were explained. The steps to be taken to increase the maintainability of the software systems can be taken at the design stage. Thus maintenance costs of software systems can be minimized. To that aim applying some techniques and principles is essential when developing software systems. The SOLID Principles are very efficient when it comes to solving such design issues and increasing maintainability of software systems. SOLID stands for five principles, namely Single responsibilities principle, Open close principle, Liskov substitution principle, Interface segregation principle, and Dependency inversion principle. Application of SOLID principles when developing software systems via object-oriented programming facilitates improving critical factors such as maintainability, extendability, readability, and reducing code complexity and tight coupling, increasing cohesion \cite{26}. Recalling from the previous sections, factors such as maintainability, extendability, readability, increasing cohesion and reducing code complexity and tight coupling are closely related to the challenges that are faced when developing Android applications. Thus it is wise to use programming techniques that can ensure the application of SOLID principles when developing Android applications. A detailed description of the SOLID principles is beyond the scope of this study. However, briefly summarizing each principle as below will be enough to remind the principles given that the readers of this study are already aware of them. Following are the brief descriptions of each principle \cite{26}:
\begin{itemize}
    \item \textbf{The Single Responsibility Principle:} A class should have only one reason to chance.
    \item \textbf{The Open/Close Principle:} A module should be open for extension but closed for modification
    \item \textbf{The Liskov Substitution Principle:} Subclasses should be substitutable for their base classes.
    \item \textbf{The Interface Segregation Principles:} Many client specific interfaces are better than one general purpose interface 
    \item \textbf{The Dependency Inversion Principle:} Depend upon Abstractions. Do not depend upon concretions
\end{itemize}
Not following SOLID principles may lead to serious maintainability problems in the software development lifecycle, such as tight coupling, code duplication, and bug fixing. Application of SOLID design principles when developing software systems helps to achieve essential quality factors such as understandability, flexibility, maintainability, and testability \cite{26}.