It was mentioned that it is important to know the applications' situation and the technology and principles used to understand the quantitative measurement results better. Knowing which features of the applications will be compared is also important to interpret the results better and comment on the evaluation's effectiveness. As stated in the previous section, the development of only four features of the cb-2 has been completed. Therefore, while quantitative measurements were being made, the evaluation was only be made over the features that have been developed in both cb-1 and cb-2, namely, splash, login, register and homepage features. So, the other features of cb-1 were ignored when making the quantitative evaluation and then the comparison. It would not be wrong to say that this situation negatively affects the efficiency of quantitative evaluation and comparison because the features used when making the evaluation are less complicated than the other application features. Although using relatively less complicated features while making the assessment slightly reduces the results' effectiveness, it does not mean that these results are false or unrealistic. However, this situation is the study's biggest limitation and gives an idea of future study subjects. As a result, the metrics, whose details are shared in section 3.2, have been applied to these four different features of two code bases. 

Presentation of the results is done as explained below. The charts and the numeric metrics values obtained from the evaluation have been shared for the project level. Although these techniques can be applied at the class and package level, it was preferred to present the project level results. It would not be very effective and useful to present these results for each class and package since there are many classes and packages for both codebases. On the other hand, at the class level, for making some evaluation and comparison, a few sample classes with high functionality were selected from both codebases, and they were evaluated and compared. Also, in accordance with the confidentiality requirements, the package and class names that will call the application name were hidden in the shared analysis results and figures. Then the results were presented via visualisation methods and numeric values. In the following sections, the results of this evaluation and the findings for comparisons are shared.