It was mentioned that it is important to know the applications' situation and the technology and principles used during the development of the applications to understand the quantitative measurement results better. In addition to this, knowing which features of the applications will be compared is also important to interpret the results better and comment on the evaluation's effectiveness. As stated in the previous paragraph, the development of only four features of the code-base-2 has been completed. Therefore, while quantitative measurements were being made, the evaluation was only be made over the features that have been developed in the code-base-2. In other words, object-oriented quality and maintainability metrics were applied to splash, login, register and homepage features of both code-base-1 and code-base-2. To have a more efficient comparison of the results, applying the metrics to only the intersection of both code bases' fully functional features was essential. So, the other fully functional features of code-base-1 were ignored when making the quantitative evaluation and then the comparison. Only these previously mentioned four features were included in the evaluation of code-base-1, and the rest of the features were removed. These removed features had no impact on the results of evaluation of code-base-1. It would not be wrong to say that this situation negatively affects the efficiency of quantitative evaluation and comparison because the features mentioned above and used when making the evaluation are less complicated than the rest of the application. Although the use of relatively less complicated features while making the assessment slightly reduces the results' effectiveness, it does not mean that these results are false or unrealistic. However, this situation draws attention to the study's biggest limitation and gives an idea of what future study subjects may be. As a result, the metrics, whose details are shared in section 3.2, have been applied to these four different code bases' features. The quantitative evaluation and comparison in this study were made as was explained above.