When other academic studies dealing with the measurement of maintainability in Android or other software systems are considered, it can be seen that many studies use scientific and quantitative methods. The work of Verdecchia et al. in the maintainability and architecture of Android applications can be shown as a successful example of this situation \cite{14}. Although it cannot be claimed that such quantitative measurements are wrong, it would not be wrong to say that these measures are inadequate at times. It is essential to make qualitative evaluations, and quantitative evaluations in areas where technologies are rapidly developing and trends change quickly, especially in Android application development. In this way, it may be possible to measure developers' experiences that differ in the face of rapid change and development and the effects of these experiences on the maintainability issue we are working on more efficiently. For these reasons, it was deemed appropriate to add a qualitative evaluation technique to this study’s scope. An Android developer survey and some interviews were conducted within this study's scope as a part of qualitative evaluations. The contents and purposes of these surveys and conferences are discussed in detail in their respective sub-sections below.

\subsubsection{Android Developer Survey}
\input{chapters/3-research-methodology/3.1-qualitative-method/3.1.1-text}

\subsubsection{Interviews with Team Members}
\input{chapters/3-research-methodology/3.1-qualitative-method/3.1.2-text}
