The second step of the qualitative evaluations carried out within this study’s scope is the interviews conducted with Mooncascade's Android team members. Unlike the Android developer survey that was explained in the previous section, these interviews are designed and conducted to qualitatively evaluate the techniques, technologies, and methods used by Mooncascade's Android team in terms of maintainability. Eight questions were determined to qualitatively measure the effect of the methods used by Mooncascade's Android team on the maintainability of Android applications. Below are listed the questions asked to each member of Mooncascade's Android team during these interviews:
\begin{itemize}
    \item How many years of experience do you have as an Android developer? Please specify the years in Mooncascade and other companies.
    \item How many different Android projects have you completed in Mooncascade, and how many different domains did those projects belong to?
    \item What is your understanding of maintainability in the context of software engineering?
    \item As an employee of a software development company that provides services to the different domains, what makes maintainability more essential for you?
    \item What is the importance of maintainability when developing Android applications?
    \item What is the most critical aspect for maintainability when developing Android applications (e.g. architecture, libraries, programming language, etc.)?
    \item How do you think the current technology stack of the team impacts Android applications’ maintainability? Please specify for each item below:
    \begin{itemize}
        \item Programming Languages(Kotlin/Java)
        \item Software Engineering principles (SOLID/Clean Code)
        \item Architecture (MVVM/Clean)
        \item Libraries (RxJava, Dagger 2, Apollo/Retrofit)
        \item Android Architecture Components (ViewModel, LiveData, Room, etc.)
    \end{itemize}
    \item What could be improved in our current tech stack and the principles we apply to improve the Android applications’ maintainability?
\end{itemize}

Three main criteria were taken into consideration while preparing these questions. First of all, questions were chosen to measure the participants' background, experience, and understanding of the concept of maintainability in software engineering. Subsequently, questions were drafted about technology and principles that directly or naturally affect maintainability. Finally, questions were prepared concerning the Android developer questionnaire, which was mentioned in the previous section, to make it possible to compare the results of both the survey and the interviews in the evaluation section. These questions, which are included in the interviews, were directed to the team members in the meetings conducted privately with each team member. The collected answers and information will be interpreted in detail in section \ref{section:5}. It is aimed that the knowledge and experience gathered through these interviews will support the accuracy and validity of quantitative assessments.