In the last decade, the impact of smartphones on our lives has significantly increased, and smartphones and mobile applications became people's primary way of interacting with technology. This situation has made the applications that work on these smartphones a vital part of daily and business life, from ordinary people to large companies. Today, mobile applications have become one of the most critical parts of digitalisation. Notably, as a successful open-source mobile operating system, Android has been a core element of this change, and the demand for Android applications has increased. Android application development has become one of the most necessary parts of the business area with a significant market share. Today, there are more than 2.5 billion active Android devices in the world \cite{1} . Therefore, it is difficult to ignore the importance of Android application development, considering the Android operating system's market share and many people's interactions with mobile applications running on Android devices. Consequently, Android application development has become an essential topic in the IT industry and academy. However, the increasing importance of the mobile era also brought more challenges to mobile application development and, of course, to Android application development.

Today, the difficulties that arise during Android application development can be examined under four major topics. These are Android's nature and its platform-specific components, demanding business requirements and sophisticated business needs, the frequent update rate of Android applications, and lastly, growing codebases and fast-changing development teams. When developing Android applications, it is essential to facilitate these difficulties. To overcome these difficulties, "maintainability" emerges as one of the most important non-functional requirements when developing Android applications. While developing Android applications, it is wise to use the technologies and techniques to increase the Android application's maintainability. Developing high-quality applications that can survive in the competitive Android market and achieving these goals in a time and cost-effective manner is only possible in this way.

This study's primary purpose is to identify and explain the methodologies and technologies used by Mooncascade, a leading software product development company with global reach, to develop real-world enterprise Android applications and evaluate these methodologies and technologies in terms of maintainability. To that aim, both qualitative analyses (in the forms of interviews, questionnaires for measuring the impact from the software complexity point of view) and quantitative analysis (measuring maintainability via object oriented software quality metrics) will be conducted.

Considering the scarcity of academic studies in this field and the inadequacy of these studies' content, and actuality problems, it can be said that this study will make a significant contribution to the academic studies in the Android field. The inadequacy and not being up-to-date with academic studies in the Android field are among the main motivations for creating this study. Another important source of motivation for this study is the negative effects of the problems arising from the lack of maintainability in Android application development on the developer experiences and the elimination of these negative effects and thus, to improve  Android developer experience.

The target audience of this study includes Android developers and researchers who are already experienced with Android application development basics and willing to learn advanced techniques and tools for Android application development. The study facilitates developers and researchers to follow the most up-to-date software engineering and Android development practices to develop state-of-the-art Android applications with high maintainability. The study only focuses on native Android application development.

\subsection{Problem Statement}
\input{chapters/1-introduction/1.1-problem-statement/1.1-text}

\subsection{Scope and Goal}
\input{chapters/1-introduction/1.2-scope-and-goal/1-2.text}

\subsection{Contributions}
\input{chapters/1-introduction/1.3-contributions/1.3-text}

\subsection{Thesis Outline}
\input{chapters/1-introduction/1.4-thesis-outline/1.4-text}